ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-20 pyked.tex
fixed my address
Add info about some of the keys in the ChemKED file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is licensed under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by/4.0/.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{ussci}

%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

\affil[1]{Department of Mechanical Engineering, University of Connecticut, Storrs, CT, USA}
\affil[2]{Mechanical, Industrial, and Manfacturing Engineering, Oregon State University, Corvalis, OR, USA}
\affil[*]{Corresponding author: \email{bryan.weber@uconn.edu}}

@@

%====================================================================
\section{Introduction}
%

\section{Conclusions}
%
\blindtext

\blindtext

\section{Acknowledgements}
This research was funded by \ldots

\printbibliography[heading=bibintoc]

>>>>

% !TEX option = -shell-escape
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is licensed under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by/4.0/.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{ussci}

\usepackage{todonotes}
\newcommand\ck{ChemKED}
\usepackage[inline]{enumitem}
\setlist{noitemsep}
%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

\affil[1]{Department of Mechanical Engineering, University of Connecticut, Storrs, CT, USA}
\affil[2]{School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University, Corvallis, OR, USA}
\affil[*]{Corresponding author: \email{bryan.weber@uconn.edu}}

@@

%====================================================================
\section{Introduction}
%
\todo[inline]{Kyle to do}

%====================================================================
\section{Related work}
%
\todo[inline]{Kyle to do}

%====================================================================
\section{Overview of format}\label{sec:overview-of-format}

The \ck{} file is a YAML-format file. This format offers the advantage of being
human readable, written in plain text, and having parsers in most common
programming languages, including Python, C++, Java, Perl, MATLAB, and many
others. The YAML syntax is quite simple. The basic file structure is made of
mappings, delimited by a colon. The key for the mapping is on the left of the
colon, and the value on the right can be a single value, a sequence of values, or a nested mapping:

\begin{minted}{yaml}
    key1: value  # Single-value mapping
    key2: [0, 1, 2]  # Mapping with sequence
    key3:  # Alternative sequence format
      - 0
      - 1
    key4:  # Nested mapping
      key5: 0
\end{minted}

The \yaml|value| can be a string, integer, or floating point number. The type is
inferred from the \yaml|key| when the value is read. The \ck{} format is
designed to include all of the information necessary to simulate a given
experiment. The \ck{} format can be broken into two main sections. The first
section details all of the ``meta'' information about the experiment and the
\ck{} file. In this section, the common \yaml|author| mapping is used for any
fields where an author must be specified. The \yaml|author| mapping contains the
following fields:
%
\begin{itemize}
    \item \yaml|name| (required, string): The author's full name
    \item \yaml|ORCID| (optional, string): the author's ORCID number
\end{itemize}
%
More generally for the meta information, the required keys in this section
are:
%
\begin{itemize}
    \item \yaml|file-author| (required, \yaml|author|-type mapping): The author
    of the \ck{} file
    \item \yaml|file-version| (required, integer): The version of the \ck{} file
    \item \yaml|chemked-version| (required, string): The version of the \ck{}
    schema that this file conforms to
    \item \yaml|reference| (required, mapping): The reference information for
    the article associated with the data in the file. The fields in this
    mapping are:
    \begin{itemize}
        \item \yaml|authors| (required, sequence): A sequence of \yaml|author| mappings
        \item \yaml|journal| (required, string): The name of the publishing journal
        \item \yaml|year| (required, integer): The year of publication
    \end{itemize}
    \item \yaml|experiment-type| (required, string): One of \yaml|ignition delay| or \yaml|flame speed|
    \item \yaml|apparatus| (required, string): The type of apparatus used to perform the experiment
\end{itemize}

In addition to the meta information, the data encoded in the \ck{} file is in
a mapping called \yaml|datapoints|. The \yaml|datapoints| mapping contains a
sequence of nested mappings, with the following information for each element of
the sequence:
%
\begin{itemize}
    \item \yaml|temperature| (required, sequence): The temperature of the experiment, with units
    \item \yaml|ignition-delay| (optional, sequence): The ignition delay of the experiment, with units, if the \yaml|experiment-type| is \yaml|ignition delay|
    \item \yaml|flame-speed| (optional, sequence): The flame speed of the experiment, with units, if the \yaml|experiment-type| is \yaml|flame speed|
    \item \yaml|pressure| (required, string): The pressure of the experiment, with units
    \item \yaml|composition| (required, sequence): The composition of the mixture in the experiment, a sequence of mappings with the following fields
    \begin{itemize}
        \item \yaml|species-name| (required, string): The name of the species
        \item \yaml|mole-fraction|, \yaml|mass-fraction|, \yaml|mole-percent| (required, float): The mole fraction or percent, or the mass fraction. Only one of the three is permitted in a given \yaml|composition| sequence.
    \end{itemize}
    \item \yaml|ignition-type| (required, mapping); The type of ignition measured in the experiments. The required fields are
    \begin{itemize}
        \item \yaml|type| (required, string): How the ignition delay was measured, one of \yaml|d/dt max| to indicate the ignition point is found at the maximum of the time derivative of the \yaml|target|, or \yaml|max| or \yaml|min| to indicate the ignition point is at the maximum or minimum of the \yaml|target|
        \item \yaml|target| (required, string): The target for the type of the ignition point, one of \yaml|temperature|, \yaml|pressure|, \yaml|OH|, \yaml|OH*|, \yaml|CH|, or \yaml|CH*|
    \end{itemize}
\end{itemize}

%====================================================================
\section{PyKED Architecture}
%
\todo[inline]{Bryan to do}

%====================================================================
\section{Use example}
%
\todo[inline]{Bryan/Kyle to do}

%====================================================================
\section{Conclusions and future work}
%
\todo[inline]{both to do}

%====================================================================
\section{Acknowledgements}
This research was funded by \ldots
\todo[inline]{update}

\printbibliography
